StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-10 paper/paper.tex
Rework section 3

\section{Design}
\label{sec:design}
StreamReduce is a distributed system for processing streams that can choose to kill tasks or
limit the amount of work it performs per task. Its design is modular and there are five
different types of nodes in a StreamReduce cluster: spout, fetcher, worker, collector, master.
\subsection{Spout}
Spouts are network-connected machines that generate data for a StreamReduce cluster to process.
Examples include a machine that tails a log file or an API like the Twitter tweet
stream. Fetchers depend on spouts as a source of streaming data.
\subsection{Fetcher}
Fetchers are responsible for communicating with spouts and returning data for the
workers to process. This level of indirection allows for a variety of different
configurations: A spout can emit data at such a high rate that using multiple fetchers
returns more data to the cluster, multiple fetchers can each talk to a different spout,
for example tailing logs from multiple machines, or fetchers can be set up redundantly
to ensure that every datum emitted by a spout is processed.

@@

Another consequence of the master being the only well-known node is that all data in the
cluster must flow through it. The master maintains two queues per job for buffering job
progress from fetchers and workers and periodically pushes this state out to workers and
collectors, respectively.
\subsection{Configuring a Cluster for a Job}
\label{sec:jobfile}
Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
running. The master must know the appropriate number of nodes to spin up; fetchers need to
know how to talk to spouts; workers need to know how to compute results; and collectors need
to know how to combine batched worker results.

>>>>

\section{Design}
\label{sec:design}
StreamReduce is a distributed system for processing streams that can choose to kill tasks or
limit the amount of work it performs per task. Its design is modular and there are five
different types of nodes in a StreamReduce cluster:
\begin{itemize}
  \item
    \textbf{Spout}: A node external to the cluster that is a source of streaming data.
  \item
    \textbf{Fetcher}: Communicates with spouts to provide data for workers.
  \item
    \textbf{Worker}: Processes data returned by fetchers. They are the source of parallel computation
    in the cluster.
  \item
    \textbf{Collector}: Aggregates results from all workers and makes the result accessible via an API.
  \item
    \textbf{Master}: Manages the cluster by bringing nodes online to complete jobs. It is reponsible
    for all internode communication and storing to-be-processed data in several queues.
\end{itemize}
Figure~\ref{fig:systemdiagram} shows a system diagram of StreamReduce.

\begin{figure*}
\includegraphics[width=\textwidth]{system-diagram.png}
\caption{Overview of data flow in the execution of a StreamReduce job. Load shedding occurs at point A. Task killing occurs at point B.}
\label{fig:systemdiagram}
\end{figure*}

\subsection{Spout}
Spouts are network-connected machines that generate data for a StreamReduce cluster to process.
Examples include a machine that tails a log file or an API like the Twitter tweet
stream. Fetchers depend on spouts as a source of streaming data.
\subsection{Fetcher}
Fetchers are responsible for communicating with spouts and returning data for the
workers to process. This level of indirection allows for a variety of different
configurations: A spout can emit data at such a high rate that using multiple fetchers
returns more data to the cluster, multiple fetchers can each talk to a different spout,
for example tailing logs from multiple machines, or fetchers can be set up redundantly
to ensure that every datum emitted by a spout is processed.

@@

Another consequence of the master being the only well-known node is that all data in the
cluster must flow through it. The master maintains two queues per job for buffering job
progress from fetchers and workers and periodically pushes this state out to workers and
collectors, respectively.

\begin{figure}
\includegraphics[width=\linewidth]{master-control-queue.png}
\caption{The master communicates directly with all nodes to pass them control messages. Nodes respond directly to the master with their results.}
\label{fig:mastercontrolqueue}
\end{figure}

Figure~\ref{fig:mastercontrolqueue} shows how control messages are passed from the master
to all other nodes in the cluster. The master communicates directly to each node and nodes
reply directly to the master when they have completed their task. With these control messages,
the master advances the state of the job. Such messages include telling a fetcher to fetch data
from a spout, giving data to a worker to process, and flushing results to collectors.

\subsection{Configuring a Cluster for a Job}
\label{sec:jobfile}
Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
running. The master must know the appropriate number of nodes to spin up; fetchers need to
know how to talk to spouts; workers need to know how to compute results; and collectors need
to know how to combine batched worker results.
